OptiFit: a fast method for fitting sequences to existing OTUs for microbial ecology

### 2021-06-21 docs/slides/2021-03-11_bistro.Rmd
Reorganize figures used in slides to subdir

background-image: url("../../figures/SchlossLab.png") 
background-size: contain
background-color: "#000000"
class: inverse

@@

.pull-right[
![](../../figures/zackular-3a.jpg)
]

@@

.center[
<img src="../../figures/schloss-2016-msystems_all-method-comparison.png"  height="350"/>
]

@@

.center[
<img src="../../figures/opticlust-supp-ex.png" width="700"/>
]

>>>>

background-image: url("../../figures/for_slides/SchlossLab.png") 
background-size: contain
background-color: "#000000"
class: inverse

@@

.pull-right[
![](../../figures/for_slides/zackular-3a.jpg)
]

@@

.center[
<img src="../../figures/for_slides/schloss-2016-msystems_all-method-comparison.png"  height="350"/>
]

@@

.center[
<img src="../../figures/for_slides/opticlust-supp-ex.png" width="700"/>
]
